Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-26 analysis/paper/paper.Rnw
changed heatmaps to landscape pages

<<heat9-2, fig.height = 7, fig.width = 7, out.width = "\\textwidth">>=
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
p
@

@@

<<heat9-5, ref.label = "heat9-2">>=
@

@@

<<heat9-7, ref.label = "heat9-2">>=
@

@@

<<heat9-11, ref.label = "heat9-2">>=
@

@@

<<heat9-13, ref.label = "heat9-2">>=
@

>>>>

\begin{landscape}

<<heat9-2, fig.height = 7, fig.width = 10, out.width = "\\textwidth">>=
ord <- match(rn, rownames(pm))

pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
@

\end{landscape}

@@

\begin{landscape}

<<heat9-5, ref.label = "heat9-2", fig.height = 7, fig.width = 10, out.width="\\textwidth">>=
@

\end{landscape}

@@

\begin{landscape}

<<heat9-7, ref.label = "heat9-2", fig.height = 7, fig.width = 10, out.width="\\textwidth">>=
@

\end{landscape}

@@

\begin{landscape}

<<heat9-11, ref.label = "heat9-2", fig.height = 7, fig.width = 10, out.width="\\textwidth">>=
@

\end{landscape}

@@

\begin{landscape}

<<heat9-13, ref.label = "heat9-2", fig.height = 7, fig.width = 10, out.width="\\textwidth">>=
@

\end{landscape}
